---
title: "Homework 1"
author: "Lily Wang"
date: "9/14/2020"
output: github_document
---

This is my solution to HW1.

```{r libraries}
library(tidyverse)
```


## Problem 1

First part of Problem 1, creating a data frame with the required elements: 

```{r create_df}
prob1_df <- tibble(
  vec_numeric = rnorm(10),
  vec_gt_0 = vec_numeric > 0,
  vec_character = c("q","w","e","r","t","y","u","i","o","p"),
  vec_factor = factor(c("low","high","mod","high","mod","mod","low","mod","low","high"))
)
prob1_df
```

Take the mean of each variable from my dataframe.

```{r means}
mean(pull(prob1_df, vec_numeric))
mean(pull(prob1_df, vec_gt_0))
mean(pull(prob1_df, vec_character))
mean(pull(prob1_df, vec_factor))
```

As seen from the warning messages, only taking the mean of the numeric and logical vectors work. 

Now, I will convert the logical, character, and factor vectors into numeric without showing the results:

```{r convert_numeric, echo = FALSE}
as.numeric(pull(prob1_df, vec_gt_0))
as.numeric(pull(prob1_df, vec_character))
as.numeric(pull(prob1_df, vec_factor))
```
The character vector could not be coerced into numeric, but the factor vector could, which does not explain what happens when I tried to take the mean as the mean could not be calculated for the factors.

Now I will convert and multiply by the random sample as directed:

```{r}
as.numeric(pull(prob1_df, vec_gt_0)) * pull(prob1_df, vec_numeric)
as.factor(pull(prob1_df, vec_gt_0)) * pull(prob1_df, vec_numeric)
as.numeric(as.factor(pull(prob1_df, vec_gt_0))) * pull(prob1_df, vec_numeric)
```



## Problem 2

Load the penguins dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

The size of this dataset is `r nrow(penguins)` rows by `r ncol(penguins)` columns. The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)` mm.
