---
title: "Homework 1"
author: "Lily Wang"
date: "9/14/2020"
output: github_document
---

This is my solution to HW1.

```{r libraries}
library(tidyverse)
```


## Problem 1

First part of Problem 1, creating a data frame with the required elements: 

```{r create_df}
prob1_df <- tibble(
  vec_numeric = rnorm(10),
  vec_gt_0 = vec_numeric > 0,
  vec_character = c("q","w","e","r","t","y","u","i","o","p"),
  vec_factor = factor(c("low","high","mod","high","mod","mod","low","mod","low","high"))
)
prob1_df
```

Take the mean of each variable from my dataframe.

```{r means}
mean(pull(prob1_df, vec_numeric))
mean(pull(prob1_df, vec_gt_0))
mean(pull(prob1_df, vec_character))
mean(pull(prob1_df, vec_factor))
```

As seen from the warning messages, only taking the mean of the numeric and logical vectors work. 

Now, I will convert the logical, character, and factor vectors into numeric without showing the results:

```{r convert_numeric, echo = FALSE}
as.numeric(pull(prob1_df, vec_gt_0))
as.numeric(pull(prob1_df, vec_character))
as.numeric(pull(prob1_df, vec_factor))
```
The character vector could not be coerced into numeric, but the factor vector could, which does not explain what happens when I tried to take the mean as the mean could not be calculated for the factors.

Now I will convert and multiply by the random sample as directed:

```{r}
as.numeric(pull(prob1_df, vec_gt_0)) * pull(prob1_df, vec_numeric)
as.factor(pull(prob1_df, vec_gt_0)) * pull(prob1_df, vec_numeric)
as.numeric(as.factor(pull(prob1_df, vec_gt_0))) * pull(prob1_df, vec_numeric)
```



## Problem 2

Load the **penguins** dataset:

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

The **penguins** dataset is `r nrow(penguins)` rows by `r ncol(penguins)` columns and contains information for the following: **`r names(penguins)`**. 

**`r names(penguins)[1]`**: Categorical. Species of penguins studied. Possible values are: `r unique(pull(penguins, species))`. \
**`r names(penguins)[2]`**: Categorical. Island where data were acquired from. Possible values are: `r unique(pull(penguins, island))`. \
**`r names(penguins)[3]`**: Double. Length of the penguin's bill in millimeters. \
**`r names(penguins)[4]`**: Double. Depth of the penguin's bill in millimeters. \
**`r names(penguins)[5]`**: Integer. Length of the penguin's flipper in millimeters. \
**`r names(penguins)[6]`**: Integer. Penguin's body mass in grams. \
**`r names(penguins)[7]`**: Categorical. Penguin's sex. Possible values are: `r unique(na.omit(pull(penguins, sex)))`. \
**`r names(penguins)[8]`**: Integer. Year in which the data were collected.

The mean flipper length is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)` mm.

Scatter plot of **flipper length vs bill length by species**:

```{r penguins_plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("bill_lengthVSflipper_length_plot.pdf", height = 4, width = 6)
```

